---
title: "Stochastic Mortality"
author: "Zakaria Al Azhar"
date: "May 20, 2018"
output: html_document 
---
---

#Introduction

This package is a practical implemenation of the stochastic mortality model as published by the Dutch Actuarial Assocation (Actuarieel Genootschap) in R. The model can be used to generate  best-estimates as well as uncertainty (quantiles) of various actuarial variables. The full publication of the stochastic mortality model (in Dutch) can be found at [ag-ai.nl](https://www.ag-ai.nl/view.php?action=view&Pagina_Id=731)

#Theoretical background


For ages (x < 90 ) and year (t >= $T_{model}$ where  $T_{model} in {2013,2016} ): 



$ln\ \mu_x(t) = Mortality \ intensitiy \ (t) =  ln\ \mu{^{EU}_x(t)} + ln\ \mu{^{NL}_x(t)  }$

$ln\ \mu_x(t) = Mortality \ intensitiy \ (t) =  ln\ \mu{^{EU}_x(t)} + ln\ \mu{^{NL}_x(t)  }$

$ln\ \mu_x(t) = Mortality \ intensitiy \ (t) =  \mu{^{EU}_x(t)} + \mu{^{NL}_x(t)  }$


$x_2$

---

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
